---
title: "Alcohol vs Seat choice"
author: "Kimberly Orantes"
date: "October 11, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The fancy boxplot reinforces the previous bocplot that shows the median of the average use of alcohol is greater for students sitting in the back than the students sitting in the front seat. The fancy boxplot's niches shows how large the standard deviation is for students sitting in the back drink more than the other students.  

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The students in the front on average consume alcohol 1.8 times a week, the students in the middle consume on average 3.3 times a week, and the students in the back consume on average 8.5 times a week. The standard deviation for the front is 3.8, the middle is 6.2, and the back is 12.5. This reinforces the second boxplot with the students sitting farther back from the front consume more alcohol.  

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is low for the anova test which means we are not done yet. The p-value means that there are at least two rows where the alcohol consumption is significantly different between them.  

```{r}
plot(TukeyHSD(model1))
```

The three seats each have a different mean level. The front to back mean level is around from 12 to 4 drinks than the front is. The back is drinking around 10 to 3 drinks more than the middle. It doesn't appear to be any difference between the middle and the front because 0 is inside the confidence level of the difference.   

## Conclusions

We were given a numerical by categorical problem and used a numerical by categorical helper file. We looked at each of the plots and concluded which row of students consumed more alcohol than other rows of students. We concluded that the back row of students which we checked this conclusion using the turkey HSD test.  

